
# Clicker Questions

to go with <b><a href = "https://mdsr-book.github.io/mdsr3e/" target = "_blank">Modern Data Science with R, 3rd edition</a></b> by Baumer, Kaplan, and Horton.  

<!-- the two formats are html and revealjs -->


```{=html}
<style>
.reveal ol ol {
   list-style-type: lower-alpha;
}
</style>
```


```{r}
#| echo: false
#| message: false
#| warning: false

# figure options
knitr::opts_chunk$set(warning = FALSE, message = FALSE,
  fig.width = 10, fig.asp = 0.618, out.width = "90%",
  fig.retina = 3, dpi = 300, fig.align = "center"
)

library(tidyverse)

# Make sure to put a space before and after every slide break "---"

```

---

1. What is a **SQL** server?.[^1]
   (a) A relational database management system.
   (b) A software whose main purpose is to store and retrieve data.
   (c) A highly secure server and does not allow any database file manipulation during execution.
   (d) All of the above.

[^1]: a. A relational database management system.


---

2. When was **SQL** created?[^2]
   (a) 1960s
   (b) 1970s
   (c) 1980s
   (d) 1990s
   (e) 2000s

[^2]: b. The first versions were created in the 1970s and called SEQUEL (Structured English QUEry Language).  c. **SQL** came about in particular systems in the 1980s.
   
---

3. What type of databases is **SQL** designed for?[^3]
   (a) hierarchical database management systems.
   (b) network database management systems.
   (c) object-oriented database management systems.
   (d) relational database management systems.

[^3]: d. relational database management systems.

---

4. Which is bigger:[^4]
   (a) computer's hard drive / storage
   (b) computer's memory / RAM

[^4]: a. computer's hard drive / storage

---

5. Where are each stored?[^5]
   (a) **SQL** `tbl` and **R**  `tibble` both in storage
   (b) **SQL** `tbl` and **R**  `tibble` both in memory
   (c) **SQL** `tbl` in storage and **R**  `tibble` in memory
   (d) **SQL** `tbl` in memory and **R**  `tibble` in storage
   
[^5]: c. **SQL** `tbl` in storage and **R**  `tibble` in memory

---

6. Which **SQL** clause is used to extract data from a database?[^6]
   (a) OPEN
   (b) EXTRACT
   (c) SELECT
   (d) GET

[^6]: c. SELECT

---

7. With SQL, how to you retrieve a column named "FirstName" from a table named "Persons"?[^7]
   (a) `SELECT` Persons.FirstName
   (b) EXTRACT FIRSTNAME `FROM` Persons
   (c) `SELECT` FirstName `FROM` Persons
   (d) `SELECT` "FirstName" `FROM` "Persons"

[^7]: c. `SELECT` FirstName `FROM` Persons

---

8. With SQL, how do you select all the columns from a table named "Persons"?[^8]
   (a) `SELECT` Persons
   (b) `SELECT` * `FROM` Persons
   (c) `SELECT` [all] `FROM` Persons
   (d) `SELECT` *.Persons

[^8]: b. `SELECT` * `FROM` Persons

---

9. With **SQL**, how can you return the number of records in the "Persons" table?[^9]
   (a) `SELECT` `COLUMNS(*)` `FROM` Persons
   (b) `SELECT` `COUNT(*)` `FROM` Persons
   (c) `SELECT` `NO(*)` `FROM` Persons
   (d) `SELECT` `LEN(*)` `FROM` Persons

[^9]: b. `SELECT` `COUNT(*)` `FROM` Persons

---

10. With **SQL**, how do you select all the records from a table named "Persons" where the value of the column "FirstName" is "Peter"?[^10]
   (a) `SELECT` * `FROM` Persons `WHERE` FirstName <> 'Peter'
   (b) `SELECT` * `FROM` Persons `WHERE` FirstName = 'Peter'
   (c) `SELECT` * `FROM` Persons `WHERE` FirstName == 'Peter'
   (d) `SELECT` [all] `FROM` Persons `WHERE` FirstName `LIKE` 'Peter'
   (e) `SELECT` [all] `FROM` Persons `WHERE` FirstName = 'Peter'
   
[^10]: b. `SELECT` * `FROM` Persons `WHERE` FirstName = 'Peter' (d. would also work.)

---

11. With SQL, how do you select all the records from a table named "Persons" where the "FirstName" is "Peter" and the "LastName" is "Jackson"?[^11]
   (a) `SELECT` FirstName = 'Peter', LastName = 'Jackson' `FROM` Persons
   (b) `SELECT` * `FROM` Persons `WHERE` FirstName <> 'Peter' AND LastName <> 'Jackson'
   (c) `SELECT` * `FROM` Persons `WHERE` FirstName = 'Peter' AND LastName = 'Jackson'
   (d) `SELECT` * `FROM` Persons `WHERE` FirstName == 'Peter' AND LastName == 'Jackson'

[^11]: c. `SELECT` * `FROM` Persons `WHERE` FirstName = 'Peter' AND LastName = 'Jackson'

---

12. Which operator selects values within a range?[^12]
    (a) `BEWTEEN`
    (b) `WITHIN`
    (c) `RANGE`

[^12]: a. `BEWTEEN`

---

13. With **SQL**, how do you select all the records from a table named "Persons" where the "LastName" is alphabetically between (and including) "Hansen" and "Pettersen"?[^13]
    (a) `SELECT` LastName > 'Hansen' AND LastName < 'Pettersen' `FROM` Persons
    (b) `SELECT` * `FROM` Persons `WHERE` LastName BETWEEN 'Hansen' AND 'Pettersen'
    (c) `SELECT` * `FROM` Persons `WHERE` LastName > 'Hansen' AND LastName < 'Pettersen'

[^13]: b. `SELECT` * `FROM` Persons `WHERE` LastName BETWEEN 'Hansen' AND 'Pettersen'

---

14. Which **SQL** statement returns only different values?[^14]
    (a) `SELECT` `UNIQUE`
    (b) `SELECT` `DISTINCT`
    (c) `SELECT` `DIFFERENT`

[^14]: b. `SELECT` `DISTINCT`

---

15. Which **SQL** keyword is used to sort the result-set?[^15]
    (a) `ORDER BY`
    (b) `ORDER`
    (c) `SORT`
    (d) `SORT BY`
 
[^15]: a. `ORDER BY`

---

16. With **SQL**, how can you return all the records from a table named "Persons" sorted descending by "FirstName"?[^16]
    (a) `SELECT` * `FROM` Persons `ORDER` FirstName `DESC`
    (b) `SELECT` * `FROM` Persons `SORT` 'FirstName' `DESC`
    (c) `SELECT` * `FROM` Persons `ORDER BY` FirstName `DESC`
    (d) `SELECT` * `FROM` Persons `SORT BY` 'FirstName' `DESC`

[^16]: c. `SELECT` * `FROM` Persons ORDER BY FirstName DESC

---

17. The OR operator displays a record if ANY conditions listed are true. The AND operator displays a record if ALL of the conditions listed are true.[^17]
    (a) TRUE
    (b) FALSE 

[^17]: a. TRUE

---

18. In order to `SELECT` the records with foods that are either green or yellow fruit:[^18] 
    (a) ... `WHERE` type = 'fruit' AND color = 'yellow' OR color = 'green'  
    (b) ... `WHERE` (type = 'fruit' AND color = 'yellow') OR color = 'green'  
    (c) ... `WHERE` type = 'fruit' AND (color = 'yellow' OR color = 'green')  
    (d) ... `WHERE` type = 'fruit' AND color = 'yellow' AND color = 'green'  
    (e) ... `WHERE` type = 'fruit' AND (color = 'yellow' AND color = 'green') 
   
[^18]: c. ... `WHERE` type = 'fruit' AND (color = 'yellow' OR color = 'green') 

---

19. What is the purpose of a `JOIN`?[^19]  
    (a) it filters the rows returned by the `SELECT` statement.
    (b) it specifies the columns to be retrieved.
    (c) it combines rows from two or more tables based on a related column.
    (d) it orders the results in ascending or descending order.

[^19]: c. it combines rows from two or more tables based on a related column.

---

20. What is the purpose of the `UNION` operator in SQL?[^20]
    (a) it combines the results of two or more `SELECT` statements. 
    (b) it performs a pattern match on a string.
    (c) it retrieves the maximum value in a column.
    (d) it filters the rows returned by the `SELECT` statement.

[^20]: a. it combines the results of two or more `SELECT` statements.

---

21. What is the purpose of the `INNER JOIN` in SQL?[^21]
    (a) it retrieves the maximum value in a column.
    (b) it combines rows from two or more tables based on a related column. 
    (c) it filters the rows returned by the `SELECT` statement.
    (d) it performs a pattern match on a string.

[^21]: b. it combines rows from two or more tables based on a related column.

---

22. What is the purpose of the `LEFT JOIN` in SQL?[^22]
    (a) it combines rows from two or more tables based on a related column.
    (b) it retrieves the maximum value in a column.
    (c) it filters the rows returned by the `SELECT` statement. 
    (d) it performs a pattern match on a string.

[^22]: a. it combines rows from two or more tables based on a related column.

---

23. `RIGHT JOIN` keeps all the rows in ...?[^23]  
    (a) the first table.
    (b) the second table.
    (c) both tables.
    (d) neither table

[^23]: a. the first table

---

24. Who is removed in a `RIGHT JOIN`?[^24]
    (a) Mick
    (b) John
    (c) Paul
    (d) Keith

```{r}
#| echo: false
#| out-width: 50%

library(cowplot)
library(ggpubr)

fig1_path <- "images/members.jpg"
fig2_path <- "images/instruments.jpg"

fig1 <- ggdraw() + draw_image(fig1_path)
fig2 <- ggdraw() + draw_image(fig2_path)

ggarrange(fig1, fig2, ncol = 2)
```

[^24]: a. Mick

---

25. Which variable(s) are removed in a `RIGHT JOIN`?[^25]
    (a) name
    (b) band
    (c) plays
    (d) none of them

```{r}
#| echo: false
#| out-width: 50%

library(cowplot)
library(ggpubr)

fig1_path <- "images/members.jpg"
fig2_path <- "images/instruments.jpg"

fig1 <- ggdraw() + draw_image(fig1_path)
fig2 <- ggdraw() + draw_image(fig2_path)

ggarrange(fig1, fig2, ncol = 2)
```

[^25]: d. none of them (all variables are kept in all joins)
 

---

26. In **SQL**, what happens to Mick's "plays" variables in a `FULL JOIN`?[^26]
    (a) Mick is removed
    (b) guitar
    (c) bass
    (d) NA
    (e) `NULL`

```{r}
#| echo: false
#| out-width: 40%

library(cowplot)
library(ggpubr)

fig1_path <- "images/members.jpg"
fig2_path <- "images/instruments.jpg"

fig1 <- ggdraw() + draw_image(fig1_path)
fig2 <- ggdraw() + draw_image(fig2_path)

ggarrange(fig1, fig2, ncol = 2)
```

[^26]: e. `NULL` (it would be NA in **R**)
 

---

<!--look at exercises: https://github.com/STAT545-UBC/STAT545-UBC-original-website/blob/master/block022_regular-expression.md

which reg expr matches all countries with "ee"

countries with "i" or "t" and ends in "land"; has "ee"; continents with "o"

can use flights data for cities with particular names-->


27. `grep("q[^u]", very.large.word.list)` would not match which of the following?[^27]
    (a) Iraqi
    (b) Iraqian
    (c) Iraq
    (d) zaqqun (tree that "springs out of the bottom of Hell", in the Quran)
    (e) Qantas (the Australian airline)
    
[^27]: neither c. nor e. would match. Inside the bracket "[^u]" matches anything other than a "u", but it has to match something.

---

28. Which of the following regex would match to both "grey" and "gray"?[^28]
    (a) "gr[ae]y"
    (b) "gr(a|e)y"
    (c) "gray | grey"
    (d) "gr[a|e]y"
    (e) some / all of the above -- which ones?

[^28]: e. all of the above. Inside a character class `|` is a normal character and would therefore match "grey" and "gray" and "gr|y".  Which is not what we want, but would work to match both "grey" and "gray".


---

29. What will the result be for the following code?[^29]  
    (a) 10
    (b) 1
    (c) 0
    (d) NA

```{r}
#| eval: false
#| echo: true
str_extract("My dog is 10 years old", "\\d")
``` 
    
[^29]: b. 1 (because `\d` matches only a single digit).


---


30. What will the result be for the following code?[^30]  
    (a) 10
    (b) 1
    (c) 0
    (d) NA

```{r}
#| eval: false
#| echo: true
str_extract("My dog is 10 years old", "\\d+")
``` 
    
[^30]: a. 10 (because `\d+` matches at least one digit).


---

31. What will the result be for the following code?[^31]
    (a) .
    (b) Episode 2: The pie whisperer. (4 August 2015)
    (c) Episode
    (d) E

```{r}
#| eval: false
#| echo: true
str_extract("Episode 2: The pie whisperer. (4 August 2015)", ".")
```

[^31]: d. E (because `.` matches anything, and returns only a single character).

---

32. What will the result be for the following code?[^32]
    (a) .
    (b) Episode 2: The pie whisperer. (4 August 2015)
    (c) Episode
    (d) E

```{r}
#| eval: false
#| echo: true
str_extract("Episode 2: The pie whisperer. (4 August 2015)", ".+")
```

[^32]: b. Episode 2: The pie whisperer. (4 August 2015) (because `.` matches anything, and with the `+` it returns multiple characters).

---

33. What will the result be for the following code?[^33]
    (a) .
    (b) Episode 2: The pie whisperer. (4 August 2015)
    (c) Episode
    (d) E

```{r}
#| eval: false
#| echo: true
str_extract("Episode 2: The pie whisperer. (4 August 2015)", "\\.")
```

[^33]: a. . (because `\.` matches the period, .).

---

34. How can I pull out just the numerical information in \$47?[^34]
    (a) "(?<=\\$)\\d"
    (b) "(?<=\\$)\\d+"
    (c) "\\d(?=\\$)"
    (d) "\\d+(?=\\$)"

```{r}
#| eval: false
#| echo: false
str_extract("$47", "(?<=\\$)\\d+")
```

[^34]: b. "(?<=\\$)\\d+"


---

35. You want to know all the types of pies in the text strings.  They are written as, for example "apple pie".[^35]
    (a) "\\w+(?!pie)"
    (b) "\\w+(?! pie)"
    (c) "\\w+(?=pie)"
    (d) "\\w+(?= pie)"

```{r}
#| eval: false
#| echo: false
str_extract(c("apple pie", "chocolate pie", "peach pie"), "\\w+(?= pie)")
```

[^35]: d. "\\w+(?= pie)"

---

```{r}
#| echo: true
str_extract(c("apple pie", "chocolate pie", "peach pie"), "\\w+(?= pie)")
```

```{r}
#| echo: true
str_extract(c("apple pie", "chocolate pie", "peach pie"), "\\w+(?=pie)")
```

---

36. We say that lookarounds are "zero-lenghth assertions".  What does that mean?[^36]
    (a) we return the string in the lookaround
    (b) we replace the string in the lookaround
    (c) we return the string at the lookaround
    (d) we replace the string at the lookaround

[^36]: c. we return the string at the lookaround


<!--
---

37. In **SQL**, which operator is used to search for a specified pattern in a column?[^57]
    (a) `LIKE`
    (b) `GET`
    (c) `FROM`

[^37]: a. `LIKE` (We didn't cover, and **SQL** has it's own characters, for example `%` for wildcard.)-->

---

37. With **SQL**, how do you select all the records from a table named "Persons" where the value of the column "FirstName" starts with an "a"?[^37]
    (a) `SELECT` * `FROM` Persons `WHERE` FirstName = 'a.*'
    (b) `SELECT` * `FROM` Persons `WHERE` FirstName = 'a*'
    (c) `SELECT` * `FROM` Persons `WHERE` FirstName `REGEXP` 'a.*'
    (d) `SELECT` * `FROM` Persons `WHERE` FirstName `REGEXP` 'a*'
    (e) `SELECT` * `FROM` Persons `WHERE` FirstName `REGEXP` '(?i)a.*'

[^37]: e. `SELECT` * `FROM` Persons `WHERE` FirstName `REGEXP` '(?i)a.*' (n.b., the `LIKE` function will give you a similar result, with `%` as a wildcard: SELECT` * `FROM` Persons `WHERE` FirstName LIKE 'a%')

---

38. What is the main way to absolutely recognize a record within a database?[^38]
    (a) Foreign key
    (b) Primary key
    (c) Unique key
    (d) Natural key
    (e) Alternate key

[^38]: b. Primary key

---

39. What does a foreign key do?[^39]
    (a) Directly identifies another table
    (b) Directly identifies another column
    (c) Gives access to another entire database
    (d) Translates the database into another language
    
[^39]: b. Directly identifies another column

---

40. Which of these would likely be used as a foreign key between a table on student enrollment and student grades?[^40]
    (a) grades
    (b) tuition
    (c) student\_name
    (d) student\_hometown
    
[^40]: c. student\_name

---

41. For the student records (for two tables: enrollment and grades), which is the most likely combination?[^41]
    (a) name as primary key to both 
    (b) name as foreign to both
    (c) name as primary in enrollment and foreign in grades
    (d) name as foreign in enrollment and primary in grades
    
[^41]: c. name as primary in enrollment and foreign in grades (the primary key must uniquely identify the records, and name is unlikely to do that in a grades database.)

---

42. Which **SQL** statement is used to create a database table called 'Customers'?[^42]
    (a) `CREATE DATABASE TAB` Customers
    (b) `CREATE DATABASE` Customers
    (c) `CREATE DATABASE TABLE` Customers
    (d) `CREATE TABLE` Customers
    (e) `CREATE DB` Customers

[^42]: d. `CREATE TABLE` Customers

---

43. Which **SQL** statement revises data in a database?[^43]
    (a) `SAVE AS` 
    (b) `MODIFY`
    (c) `SAVE`
    (d) `UPDATE`

[^43]: d. `UPDATE`

---

44. Which **SQL** statement takes out data from a database?[^44]
    (a) `REMOVE`
    (b) `DELETE`
    (c) `COLLAPSE`

[^44]: b. `DELETE`

---

45. The `NOT NULL` constraint enforces a column to not accept `NULL` values.[^45]
    (a) FALSE
    (b) TRUE

[^45]: b. TRUE

---

46. Which **SQL** statement places new data in a database?[^46]
    (a) `ADD RECORD`
    (b) `INSERT INTO`
    (c) `ADD NEW`
    (d) `INSERT NEW` 
 
[^46]: b. `INSERT INTO`

---

47. With **SQL**, how can you insert a new record into the "Persons" table?[^47]
    (a) `INSERT` `INTO` Persons VALUES ('Jimmy', 'Jackson')
    (b) `INSERT` ('Jimmy', 'Jacskon') `INTO` Persons
    (c) `INSERT` VALUES ('Jimmy', 'Jackson') `INTO` Persons

[^47]: a. `INSERT` `INTO` Persons VALUES ('Jimmy', 'Jackson')

---

48. With **SQL**, how can you insert "Olsen" as the "LastName" in the "Persons" table?[^48]
    (a) `INSERT` `INTO` Persons (LastName) VALUES ('Olsen')
    (b) `INSERT` `INTO` Persons ('Olsen) `INTO` LastName
    (c) `INSERT` ('Olsen') `INTO` Persons (LastName)
 
[^48]: a. `INSERT` `INTO` Persons (LastName) VALUES ('Olsen')

---

49. How can you change "Hansen" into "Nilsen" in the "LastName" column in the Persons table?[^49]
    (a) `MODIFY` Persons `SET` LastName='Nilsen' `WHERE` LastName='Hansen'
    (b) `UPDATE` Persons `SET` LastName='Hansen' `INTO` LastName='Nilsen'
    (c) `MODIFY` Persons `SET` LastName='Hansen' `INTO` LastName='Nilsen'
    (d) `UPDATE` Persons `SET` LastName='Nilsen' `WHERE` LastName='Hansen' 

[^49]: d. `UPDATE` Persons `SET` LastName='Nilsen' `WHERE` LastName='Hansen' 

---

50. With **SQL**, how can you delete the records where the "FirstName" is "Peter" in the Persons Table?[^50]
    (a) `DELETE` `FROM` Persons `WHERE` FirstName='Peter'
    (b) `DELETE` FirstName='Peter' `FROM` Persons
    (c) `DELETE ROW` FirstName='Peter' `FROM` Persons

[^50]: a. `DELETE` `FROM` Persons `WHERE` FirstName='Peter'

---

51. In the `flights` table, the following `INDEX`es exist: `Tailnum`, `Year`, and `Date`.  How many rows would be looked through if the `WHERE` filter was on `month` only?[^51]
    (a) more than 6.3 million
    (b) less than 6.3 million
    (c) more than 700,000
    (d) less than 700,000
    
[^51]: a. more than 6.3 million. Because there is no index on month (and we don't have a year to incorporate month into the Date index), we need to look through all 48 million rows.

---

52. Which has a larger cardinality, `Tailnum` or `Year`?[^52]
    (a) `Tailnum`
    (b) `Year`
    (c) they have the same cardinality
    (d) neither has a cardinality

[^52]: a. `Tailnum`. The cardinality is the number of unique values, and there are many more unique planes than years.


---

53. Which index takes up more storage space, the one on `Tailnum` or the one on `Year`?[^53]
    (a) `Tailnum`
    (b) `Year`
    (c) they take up the same space
    (d) you can't index on either variable

[^53]: a. `Tailnum`. Because the cardinality is higher, it will take up much more space in the index.

---

54. Which index is more effective at reducing querying time, the one on `Tailnum` or the one on `Year`?[^54]
    (a) `Tailnum`
    (b) `Year`
    (c) the queries would be the same
    (d) you can't query on either variable
    
[^54]: a. `Tailnum`. Because the index is more complete, it will make the querying more efficient.

---

55. What does the **R** function `ifelse(a, b, c)` do?[^55]
    (a) a = TRUE option, b = FALSE option, c = question
    (b) a = FALSE option, b = TRUE option, c = question
    (c) a = question, b = TRUE option, c = FALSE option
    (d) a = question, b = FALSE option, c = TRUE option

[^55]: c. a = question, b = TRUE option, c = FALSE option

---

56. What does the **R** function `case_when()` do?[^56]
    (a) renames a variable
    (b) changes the data type of a variable
    (c) partitions a numeric variable
    (d) creates a new variable by re-coding an original variable

[^56]: d. creates a new variable by re-coding an original variable

---

57. What does the **R** function `cut()` do?[^57]
    (a) renames a variable
    (b) changes the data type of a variable
    (c) partitions a numeric variable
    (d) creates a new variable by re-coding an original variable

[^57]: c. partitions a numeric variable

---





