---
title: "Schedule"
description: |
  Schedule for DS002R, Foundations of Data Science in R, Pomona College, Fall 2024
execute: 
  message: false
  warning: false
---

```{r}
#| echo: false
library(tidyverse)
#library(fontawesome)
#fontawesome::fa_html_dependency()
```

Here's your roadmap for the semester! Each day, follow the general process outlined below:

-   Enjoy the notes / text <i class="fas fa-book-open"></i>

-   Attend class, review the <i class="fas fa-pencil-alt"></i> worksheet and solutions if you have any questions after working on it during class.  <i class="fas fa-desktop"></i> Slides from class are linked below. 

-   Complete the Lab assignment (<i class="fa-solid fa-code"></i> html linked below), <i class="fa-solid fa-paper-plane"></i> submit the assignment to GitHub before 10am the following class period.

-   Discuss the reflection questions <i class="fas fa-lightbulb"></i> and ethics considerations <i class="fas fa-balance-scale"></i> (see the <i class="fas fa-book-open"></i> <a href = "https://st47s.com/SDS261/Notes/" target = "_blank">class notes</a>) with your classmates and professor.

-   The textbooks are <b> <a href = "https://mdsr-book.github.io/mdsr3e/" target = "_blank">Modern Data Science with R (MDSR), 3rd edition</a></b> by Baumer, Kaplan, and Horton and <b> <a href = "https://r4ds.hadley.nz/" target = "_blank">R for Data Science (R4DS), 2nd edition</a></b> by Wickham, Çetinkaya-Rundel, and Grolemund.

<!--
In order to use the icons, you need the fontawesome extension, https://github.com/quarto-ext/fontawesome

quarto add quarto-ext/fontawesome
-->


```{r}
#| echo: false
schedule <- tribble(
  ~`date`, ~topic, ~`in class`, ~`in lab`, ~resources,
  "Week 1 <br> 8.26.24", 'intro + <br> R + RStudio + <br> GitHub + <br> ggplot', 
  '{{< fa book-open >}} <a href="https://st47s.com/DS002R/Notes/" target = "_blank">Introduction</a> <br> {{< fa book-open >}} <a href="https://mdsr-book.github.io/mdsr3e/15-sqlI.html#sec-dplyr-sql" target = "_blank"> MDSR 15.1</a> <br> {{< fa book-open >}} <a href="https://r4ds.hadley.nz/visualize" target = "_blank"> R4DS Visualize</a> <br> {{< fa desktop >}} <a href="https://sds261-sql.netlify.app/slides/2024-01-08-db.html" target = "_blank"> What is a DB?</a> <br> {{< fa pencil >}} <a href="https://sds261-sql.netlify.app/handout/ws1_sds261_j24.pdf" target = "_blank">WS 1</a>',
  '{{< fa code >}} <a href="https://sds261-sql.netlify.app/handout/lab1_db_sds261_j24.html" target = "_blank">Lab 1</a>',
  '{{< fa comments >}} <a href = "https://dbplyr.tidyverse.org/articles/dbplyr.html" target = "_blank"><b>dbplyr</b> package</a>',
  
   "Week 2 <br> 9.2.24", 'no class Mon <br> ggplot', 
  ' ',
  ' ',
  ' ',
  
   "Week 3 <br> 9.9.24", 'tidyverse', 
  ' ',
  ' ',
  ' ',

     "Week 4 <br> 9.16.24", 'tidy strings', 
  ' ',
  ' ',
  ' ',

  
     "Week 5 <br> 9.23.24", 'map + <br>functions', 
  ' ',
  ' ',
  ' ',

  
     "Week 6 <br> 9.30.24", 'iteration + <br>simulations', 
  ' ',
  ' ',
  ' ',

  
     "Week 7 <br> 10.7.24", 'permutation tests ', 
  ' ',
  ' ',
  ' ',

  
     "Week 8 <br> 10.14.24", 'no class Mon <br> code review + <br> reprex', 
  ' ',
  ' ',
  ' ',

  
     "Week 9 <br> 10.21.24", 'web scraping', 
  ' ',
  ' ',
  ' ',

  
     "Week 10 <br> 10.28.24", 'SQL', 
  ' ',
  ' ',
  ' ',
  
  
     "Week 11 <br> 11.4.24", 'regular expressions', 
  ' ',
  ' ',
  ' ',
  
  
     "Week 12 <br> 11.11.24", 'text analysis', 
  ' ',
  ' ',
  ' ',
  
  
     "Week 13 <br> 11.18.24", ' ', 
  ' ',
  ' ',
  ' ',

     "Week 14 <br> 11.25.24", 'no class Wed <br>', 
  ' ',
  ' ',
  ' ',

     "Week 15 <br> 12.2.24", ' ', 
  ' ',
  ' ',
  ' '
)
  
```

```{r}
#| echo: false
#| column: screen-inset
# can also use column: screen-inset also the entire page??
# can use column: page for the entire page
# can use column: body-outset to bleed outside the center column of text
schedule |> 
  gt::gt() |> 
  gt::fmt_markdown(columns = everything())
```





