---
title: "Schedule"
description: |
  Schedule for DS002R, Foundations of Data Science in R, Pomona College, Fall 2025
format:
  html:
    code-fold: true
    html-math-method: katex
execute: 
  message: false
  warning: false
---


<!-- Note to self:  this broke when i upgraded the gt package above 0.11.0 (to 0.11.1).  not sure why!  didn't like the function: gt::fmt_markdown(columns = everything())  -->



```{r}
#| echo: false
library(tidyverse)
#library(fontawesome)
#fontawesome::fa_html_dependency()
```

Here's your roadmap for the semester! Each day, follow the general process outlined below:

-   Enjoy the notes / text <i class="fas fa-book-open"></i>

-   Attend class, review the <i class="fas fa-pencil-alt"></i> worksheet and solutions if you have any questions after working on it during class.  <i class="fas fa-desktop"></i> Slides from class are linked below. 

-   Discuss the reflection questions <i class="fas fa-lightbulb"></i> and ethics considerations <i class="fas fa-balance-scale"></i> (see the <i class="fas fa-book-open"></i> <a href = "https://ds002r-fds.netlify.app/notes" target = "_blank">class notes</a>) with your classmates and professor.

-   The textbooks are <b> <a href = "https://mdsr-book.github.io/mdsr3e/" target = "_blank">Modern Data Science with R (MDSR), 3rd edition</a></b> by Baumer, Kaplan, and Horton and <b> <a href = "https://r4ds.hadley.nz/" target = "_blank">R for Data Science (R4DS), 2nd edition</a></b> by Wickham, Çetinkaya-Rundel, and Grolemund.

-   Homework assignments are found at the <a href = "https://github.com/orgs/ST47S-FODS-Fall2025/repositories" target = "_blank">GitHub course organization</a>.  Due dates are provided on each assignment (roughly every other week).  See the <a href = "https://ds002r-fds.netlify.app/github">course GitHub page</a> for more information on how to find, complete, and submit assignments.

<!--
In order to use the icons, you need the fontawesome extension, https://github.com/quarto-ext/fontawesome

quarto add quarto-ext/fontawesome
-->


```{r}
#| echo: false
schedule <- tribble(
  ~`date`, ~topic, ~`class materials`, ~`due dates`, ~resources,
  "Week 1 <br> 8.25.25", 'intro + <br> R + RStudio + <br> GitHub', 
  '{{< fa book-open >}} <a href="https://st47s.com/DS002R/Notes/01-intro.html" target = "_blank">Introduction</a> <br> {{< fa book-open >}} <a href="https://mdsr-book.github.io/mdsr3e/01-intro.html" target = "_blank"> MDSR Prologue</a> <br> {{< fa book-open >}} <a href = "https://www.openscapes.org/blog/2022/05/27/github-illustrated-series/" target = "_blank">Why Git? + monsters</a> <br> {{< fa desktop >}} <a href="https://ds002r-fds.netlify.app/slides/2025-08-25-intro.html" target = "_blank"> Introduction</a> <br> {{< fa pencil >}} <a href="https://ds002r-fds.netlify.app/handout/ws1_ds2_f25_DSproj.pdf" target = "_blank">WS 1 - DS project</a> ',
  ' ',
  '{{< fa comments >}} <a href = "http://nssdeviations.com/71-compromised-shoe-situation" target = "_blank">NSSD - Compromised Shoe Situation</a>',
  
   "Week 2 <br> 9.1.25", 'Data Viz', 
  '{{< fa book-open >}} <a href="https://r4ds.hadley.nz/visualize" target = "_blank"> R4DS Visualize</a> <br> {{< fa book-open >}} <a href="https://st47s.com/DS002R/Notes/10-grammar-graphics.html" target = "_blank">graphics</a> <br> {{< fa book-open >}} <a href="https://st47s.com/DS002R/Notes/11-ggplot.html" target = "_blank">ggplot</a> <br> {{< fa desktop >}} <a href="https://ds002r-fds.netlify.app/slides/2025-09-03-dataviz.html" target = "_blank"> Data Viz</a> <br> {{< fa pencil >}} <a href="https://ds002r-fds.netlify.app/handout/ws2_ds2_f25_ggplot.pdf" target = "_blank">WS 2 - ggplot</a> ',
  '{{< fa code >}} <a href="https://github.com/orgs/ST47S-FODS-Fall2025/repositories" target = "_blank">HW 1</a> - due 9.3.25',
  '{{< fa comments >}} Tufte. 1997. <a href = "https://www.edwardtufte.com/book/visual-and-statistical-thinking-displays-of-evidence-for-making-decisions/" target = "_blank">Visual and Statistical Thinking: Displays of Evidence for Making Decisions</a>',
  
   "Week 3 <br> 9.8.25", 'Data Viz', 
  '{{< fa book-open >}} <a href="https://r4ds.hadley.nz/visualize" target = "_blank"> R4DS Visualize</a> <br> {{< fa book-open >}} <a href="https://st47s.com/DS002R/Notes/10-grammar-graphics.html" target = "_blank">graphics</a> <br> {{< fa book-open >}} <a href="https://st47s.com/DS002R/Notes/11-ggplot.html" target = "_blank">ggplot</a> <br> {{< fa desktop >}} <a href="https://ds002r-fds.netlify.app/slides/2025-09-03-dataviz.html" target = "_blank"> Data Viz</a> <br> {{< fa desktop >}} <a href="https://ds002r-fds.netlify.app/slides/2025-09-10-verbs.html" target = "_blank"> Data Verbs</a> <br> {{< fa pencil >}} <a href="https://ds002r-fds.netlify.app/handout/ws3_ds2_f25_tufte.pdf" target = "_blank">WS 3 - Tufte</a> <br> {{< fa pencil >}} <a href="https://ds002r-fds.netlify.app/handout/ws4_ds2_f25_verbs.pdf" target = "_blank">WS 4 - Data Verbs</a> ',
  '{{< fa code >}} <a href="https://github.com/orgs/ST47S-FODS-Fall2025/repositories" target = "_blank">HW 2</a> - due 9.10.25',
  ' ',

     "Week 4 <br> 9.15.25", 'Data Wrangling', 
  '{{< fa book-open >}} <a href="https://r4ds.had.co.nz/transform.html" target = "_blank"> R4DS Transform</a> <br> {{< fa book-open >}} <a href="https://st47s.com/DS002R/Notes/07-wrangling.html" target = "_blank">wrangling</a> <br> {{< fa desktop >}} <a href="https://ds002r-fds.netlify.app/slides/2025-09-15-pivotjoin.html" target = "_blank"> Pivot + Join</a> <br> {{< fa pencil >}} <a href="https://ds002r-fds.netlify.app/handout/ws5_ds2_f25_join.pdf" target = "_blank">WS 5 - Join</a>',

    '{{< fa code >}} <a href="https://github.com/orgs/ST47S-FODS-Fall2025/repositories" target = "_blank">HW 3</a> - due 9.17.25 <br> <i class="fa-regular fa-circle-question"></i> Quiz 1 9.17.25',
  ' ',

  
     "Week 5 <br> 9.22.25", 'Data Types', 
  '{{< fa book-open >}} <a href="https://r4ds.hadley.nz/factors" target = "_blank"> R4DS Factors</a> <br> {{< fa book-open >}} <a href="https://r4ds.hadley.nz/strings" target = "_blank"> R4DS Strings</a> <br> {{< fa book-open >}} <a href="https://st47s.com/DS002R/Notes/08-text-analysis.html" target = "_blank">Text analysis</a> <br> {{< fa desktop >}} <a href="https://ds002r-fds.netlify.app/slides/2025-09-22-types.html" target = "_blank">Data Types</a> <br> {{< fa pencil >}} <a href="https://ds002r-fds.netlify.app/handout/ws6_ds2_f25_strings.pdf" target = "_blank">WS 6 - Strings</a> <br> {{< fa pencil >}} <a href="https://ds002r-fds.netlify.app/handout/ws7_ds2_f25_factors.pdf" target = "_blank">WS 7 - Factors</a>',

  '<i class="fa-solid fa-chart-column"></i> <a href="https://ds002r-fds.netlify.app/project1">Project 1</a> - due 9.24.25',
  ' ',

  
     "Week 6 <br> 9.29.25", 'Regular Expressions', 
  '{{< fa book-open >}} <a href="https://r4ds.hadley.nz/regexps.html" target = "_blank"> R4DS Regular expressions</a> <br> {{< fa book-open >}} <a href="https://st47s.com/DS002R/Notes/09-reg-expr.html" target = "_blank">Regular expressions</a> <br> {{< fa desktop >}} <a href="https://ds002r-fds.netlify.app/slides/2025-09-29-regex.html" target = "_blank">Regular expressions</a> <br> {{< fa pencil >}} <a href="https://ds002r-fds.netlify.app/handout/ws8_ds2_f25_regex1.pdf" target = "_blank">WS 8 - Regular Expressions</a>',

  '{{< fa code >}} <a href="https://github.com/orgs/ST47S-FODS-Fall2025/repositories" target = "_blank">HW 4</a> - due 10.1.25 <br> <i class="fa-regular fa-circle-question"></i> Quiz 2 10.1.25',
  ' ',

  
     "Week 7 <br> 10.6.25", 'functions + <br> iteration', 
  '{{< fa book-open >}} <a href="https://r4ds.hadley.nz/functions" target = "_blank"> R4DS Fuctions</a> <br>  {{< fa book-open >}} <a href="https://r4ds.hadley.nz/iteration" target = "_blank"> R4DS Iteration</a> <br>  {{< fa book-open >}} <a href="https://st47s.com/DS002R/Notes/12-iteration.html" target = "_blank">Functions + Iteration</a> <br> {{< fa desktop >}} <a href="https://ds002r-fds.netlify.app/slides/2025-10-06-funcmap.html" target = "_blank">functions + iteration</a> <br> {{< fa pencil >}} <a href="https://ds002r-fds.netlify.app/handout/ws9_ds2_f25_funcs.pdf" target = "_blank">WS 9 - Functions</a> <br> {{< fa pencil >}} <a href="https://ds002r-fds.netlify.app/handout/ws10_ds2_f25_map.pdf" target = "_blank">WS 10 - map</a>',

    '<i class="fa-solid fa-chart-column"></i> <a href="https://ds002r-fds.netlify.app/project2">Project 2</a> - due 10.8.25',
  ' ',

  
     "Week 8 <br> 10.13.25", 'code review + <br> reprex', 
 '{{< fa book-open >}} <a href="https://www.tidyverse.org/help/" target = "_blank"> reproducible examples</a> <br>  {{< fa book-open >}} <a href="https://style.tidyverse.org/" target = "_blank"> Tidyverse style guide</a> <br>  {{< fa book-open >}} <a href="https://st47s.com/DS002R/Notes/16-reprex.html" target = "_blank">Reproducible examples</a> <br> {{< fa desktop >}} <a href="https://ds002r-fds.netlify.app/slides/2025-10-15-help.html" target = "_blank">help me help you</a> <br> {{< fa pencil >}} <a href="https://ds002r-fds.netlify.app/handout/ws11_ds2_f25_reprex.pdf" target = "_blank">WS 11 - reproducible example</a>',
  ' ',
  ' ',

     "Week 9 <br> 10.20.25", 'simulations', 
 '{{< fa book-open >}} <a href="https://mdsr-book.github.io/mdsr3e/13-simulation.html" target = "_blank"> MDSR Simulations</a> <br> {{< fa book-open >}} <a href="https://st47s.com/DS002R/Notes/12-iteration.html" target = "_blank">Simulations</a> <br> {{< fa desktop >}} <a href="https://ds002r-fds.netlify.app/slides/2025-10-20-sims.html" target = "_blank">Simulations</a> <br> {{< fa pencil >}} <a href="https://ds002r-fds.netlify.app/handout/ws12_ds2_f25_probsim.pdf" target = "_blank">WS 12 - probability simulation</a>',
  '{{< fa code >}} <a href="https://github.com/orgs/ST47S-FODS-Fall2025/repositories" target = "_blank">HW 5</a> - due <b> Monday </b> 10.20.25 <br> <i class="fa-regular fa-circle-question"></i> Quiz 3 10.22.25',

  ' ',

  
     "Week 10 <br> 10.27.25", 'permutation tests', 
 '{{< fa book-open >}} <a href="https://st47s.com/DS002R/Notes/13-permutation-tests.html" target = "_blank">Permutation tests</a> <br> {{< fa desktop >}} <a href="https://ds002r-fds.netlify.app/slides/2025-10-27-perm.html" target = "_blank">Permutation tests</a> <br> {{< fa desktop >}} <a href="https://ds002r-fds.netlify.app/slides/2025-10-29-ethics.html" target = "_blank">Data Science Ethics</a> <br> {{< fa pencil >}} <a href="https://ds002r-fds.netlify.app/handout/ws13_ds2_f25_helper.pdf" target = "_blank">WS 13 - helper vs. hinderer</a> <br> {{< fa pencil >}} <a href="https://ds002r-fds.netlify.app/handout/ws14_ds2_f25_ethics.pdf" target = "_blank">WS 14 - ethical considerations</a>',
  '<i class="fa-solid fa-chart-column"></i> <a href="https://ds002r-fds.netlify.app/project3">Project 3</a> - due 10.30.25 (<b>Thursday!</b>)',
  ' ',
  
  
     "Week 11 <br> 11.3.25", 'web scraping', 
 '{{< fa book-open >}} <a href="https://r4ds.hadley.nz/webscraping" target = "_blank">R4DS Web scraping</a> <br> {{< fa book-open >}} <a href="https://st47s.com/DS002R/Notes/03-rvest.html" target = "_blank">Web scraping</a> <br> {{< fa desktop >}} <a href="https://ds002r-fds.netlify.app/slides/2025-11-03-webscrape.html" target = "_blank">Web scraping</a> <br> {{< fa pencil >}} <a href="https://ds002r-fds.netlify.app/handout/ws15_ds2_f25_webscrapt.pdf" target = "_blank">WS 15 - web scraping</a>',
  '{{< fa code >}} <a href="https://github.com/orgs/ST47S-FODS-Fall2025/repositories" target = "_blank">HW 6</a> - due 11.5.25 <br> <i class="fa-regular fa-circle-question"></i> Quiz 4 11.5.25',

  ' ',
  
  
     "Week 12 <br> 11.10.25", 'SQL', 
 '{{< fa book-open >}} <a href="https://r4ds.hadley.nz/databases.html" target = "_blank">R4DS Databases</a> <br> {{< fa book-open >}} <a href="https://mdsr-book.github.io/mdsr3e/15-sqlI.html" target = "_blank">MDSR Database querying</a> <br> {{< fa book-open >}} <a href="https://st47s.com/DS002R/Notes/04-sql-in-R.html" target = "_blank">SQL</a> <br> {{< fa desktop >}} <a href="https://ds002r-fds.netlify.app/slides/2025-11-10-db.html" target = "_blank">SQL DBMS</a> <br> {{< fa desktop >}} <a href="https://ds002r-fds.netlify.app/slides/2025-11-12-clauses.html" target = "_blank">SQL statements</a>',
   '<i class="fa-solid fa-chart-column"></i> <a href="https://ds002r-fds.netlify.app/project4">Project 4</a> - due 11.12.25',
  ' ',
  
  
     "Week 13 <br> 11.17.25", 'SQL', 
 '{{< fa book-open >}} <a href="https://r4ds.hadley.nz/databases.html" target = "_blank">R4DS Databases</a> <br> {{< fa book-open >}} <a href="https://mdsr-book.github.io/mdsr3e/15-sqlI.html" target = "_blank">MDSR Database querying</a> <br> {{< fa book-open >}} <a href="https://st47s.com/DS002R/Notes/06-sql-joins.html" target = "_blank">SQL joins</a> <br> {{< fa desktop >}} <a href="https://ds002r-fds.netlify.app/slides/2025-11-17-joins.html" target = "_blank">SQL joins</a>',
  '{{< fa code >}} <a href="https://github.com/orgs/ST47S-FODS-Fall2025/repositories" target = "_blank">HW 7</a> - due 11.19.25 <br> <i class="fa-regular fa-circle-question"></i> Quiz 5 11.19.25',
  ' ',

     "Week 14 <br> 11.24.25", 'Shiny', 
  '{{< fa book-open >}} <a href="https://mastering-shiny.org/" target = "_blank">Matering Shiny</a> <br> {{< fa book-open >}} <a href="https://mdsr-book.github.io/mdsr3e/14-datavizIII.html#sec-shiny" target = "_blank">MDSR Interactive web apps with Shiny</a> <br> {{< fa book-open >}} <a href="https://st47s.com/DS002R/Notes/12-shiny.html" target = "_blank">Shiny</a> <br> {{< fa desktop >}} <a href="https://ds002r-fds.netlify.app/slides/2025-11-24-shiny.html" target = "_blank">Shiny</a>',
  '<i class="fa-solid fa-chart-column"></i> <a href="https://ds002r-fds.netlify.app/project5">Project 5</a> - due 11.26.25',
  ' ',

      "Week 15 <br> 12.1.25", ' ', 
  '{{< fa desktop >}} <a href="https://ds002r-fds.netlify.app/slides/2025-12-01-fin.html" target = "_blank">Fin</a> ',
   '<i class="fa-regular fa-circle-question"></i> Quiz 6 12.3.25',
  'presentations (?) 12.5.25, 9am - noon',
  
    "Week 16 <br> 12.10.25", ' ', 
  ' ',
  '<i class="fa-solid fa-chart-column"></i> <a href="https://ds002r-fds.netlify.app/project6">Project 6</a> - due 12.10.25', 'presentations (?) 12.10.25, 9am - noon'
)
  
```

```{r}
#| echo: false
#| column: screen-inset
# can also use column: screen-inset also the entire page??
# can use column: page for the entire page
# can use column: body-outset to bleed outside the center column of text
schedule |> 
  gt::gt() |> 
  gt::fmt_markdown(columns = everything()) |> 
    gt::cols_width(date ~ pct(8),
                 everything() ~ pct(23)) 
```





