---
title: "Schedule"
description: |
  Schedule for DS002R, Foundations of Data Science in R, Pomona College, Spring 2025
format:
  html:
    code-fold: true
    html-math-method: katex
execute: 
  message: false
  warning: false
---


<!-- Note to self:  this broke when i upgraded the gt package above 0.11.0 (to 0.11.1).  not sure why!  didn't like the function: gt::fmt_markdown(columns = everything())  -->



```{r}
#| echo: false
library(tidyverse)
#library(fontawesome)
#fontawesome::fa_html_dependency()
```

Here's your roadmap for the semester! Each day, follow the general process outlined below:

-   Enjoy the notes / text <i class="fas fa-book-open"></i>

-   Attend class, review the <i class="fas fa-pencil-alt"></i> worksheet and solutions if you have any questions after working on it during class.  <i class="fas fa-desktop"></i> Slides from class are linked below. 

-   Discuss the reflection questions <i class="fas fa-lightbulb"></i> and ethics considerations <i class="fas fa-balance-scale"></i> (see the <i class="fas fa-book-open"></i> <a href = "https://ds002r-fds.netlify.app/notes" target = "_blank">class notes</a>) with your classmates and professor.

-   The textbooks are <b> <a href = "https://mdsr-book.github.io/mdsr3e/" target = "_blank">Modern Data Science with R (MDSR), 3rd edition</a></b> by Baumer, Kaplan, and Horton and <b> <a href = "https://r4ds.hadley.nz/" target = "_blank">R for Data Science (R4DS), 2nd edition</a></b> by Wickham, Çetinkaya-Rundel, and Grolemund.

-   Homework assignments are found at the <a href = "https://github.com/orgs/ST47S-FODS-Spring2025/repositories" target = "_blank">GitHub course organization</a>.  Due dates are provided on each assignment (roughly every other week).  See the <a href = "https://ds002r-fds.netlify.app/github">course GitHub page</a> for more information on how to find, complete, and submit assignments.

<!--
In order to use the icons, you need the fontawesome extension, https://github.com/quarto-ext/fontawesome

quarto add quarto-ext/fontawesome
-->


```{r}
#| echo: false
schedule <- tribble(
  ~`date`, ~topic, ~`class materials`, ~`due dates`, ~resources,
  "Week 1 <br> 1.22.25", 'intro + <br> R + RStudio + <br> GitHub', 
  '{{< fa book-open >}} <a href="https://st47s.com/DS002R/Notes/01-intro.html" target = "_blank">Introduction</a> <br> {{< fa book-open >}} <a href="https://mdsr-book.github.io/mdsr3e/01-intro.html" target = "_blank"> MDSR Prologue</a> <br> {{< fa book-open >}} <a href = "https://www.openscapes.org/blog/2022/05/27/github-illustrated-series/" target = "_blank">Why Git? + monsters</a> <br> {{< fa desktop >}} <a href="https://ds002r-fds.netlify.app/slides/2025-01-22-intro.html" target = "_blank"> Introduction</a> <br> {{< fa pencil >}} <a href="https://ds002r-fds.netlify.app/handout/ws1_ds2_s25_DSproj.pdf" target = "_blank">WS 1 - DS project</a> ',
  ' ',
  '{{< fa comments >}} <a href = "http://nssdeviations.com/71-compromised-shoe-situation" target = "_blank">NSSD - Compromised Shoe Situation</a>',
  
   "Week 2 <br> 1.27.25", 'Data Viz', 
  '{{< fa book-open >}} <a href="https://r4ds.hadley.nz/visualize" target = "_blank"> R4DS Visualize</a> <br> {{< fa book-open >}} <a href="https://st47s.com/DS002R/Notes/10-grammar-graphics.html" target = "_blank">graphics</a> <br> {{< fa book-open >}} <a href="https://st47s.com/DS002R/Notes/11-ggplot.html" target = "_blank">ggplot</a> <br> {{< fa desktop >}} <a href="https://ds002r-fds.netlify.app/slides/2025-01-27-dataviz.html" target = "_blank"> Data Viz</a> <br> {{< fa pencil >}} <a href="https://ds002r-fds.netlify.app/handout/ws2_ds2_s25_R.pdf" target = "_blank">WS 2 - R</a> <br> {{< fa pencil >}} <a href="https://ds002r-fds.netlify.app/handout/ws3_ds2_s25_tufte.pdf" target = "_blank">WS 3 - Tufte</a>',
  '{{< fa code >}} <a href="https://github.com/orgs/ST47S-FODS-Spring2025/repositories" target = "_blank">HW 1</a> - due 1.30.25 (Thursday!)',
  '{{< fa comments >}} Tufte. 1997. <a href = "https://www.edwardtufte.com/book/visual-and-statistical-thinking-displays-of-evidence-for-making-decisions/" target = "_blank">Visual and Statistical Thinking: Displays of Evidence for Making Decisions</a>',
  
   "Week 3 <br> 2.3.25", 'Data Viz', 
  '{{< fa book-open >}} <a href="https://r4ds.hadley.nz/visualize" target = "_blank"> R4DS Visualize</a> <br> {{< fa book-open >}} <a href="https://st47s.com/DS002R/Notes/10-grammar-graphics.html" target = "_blank">graphics</a> <br> {{< fa book-open >}} <a href="https://st47s.com/DS002R/Notes/11-ggplot.html" target = "_blank">ggplot</a> <br> {{< fa desktop >}} <a href="https://ds002r-fds.netlify.app/slides/2025-01-27-dataviz.html" target = "_blank"> Data Viz</a> <br> {{< fa desktop >}} <a href="https://ds002r-fds.netlify.app/slides/2025-02-05-verbs.html" target = "_blank"> Data Verbs</a> <br> {{< fa pencil >}} <a href="https://ds002r-fds.netlify.app/handout/ws4_ds2_s25_ggplot.pdf" target = "_blank">WS 4 - ggplot</a> <br> {{< fa pencil >}} <a href="https://ds002r-fds.netlify.app/handout/ws5_ds2_s25_verbs.pdf" target = "_blank">WS 5 - Verbs</a>',
  '{{< fa code >}} <a href="https://github.com/orgs/ST47S-FODS-Spring2025/repositories" target = "_blank">HW 2</a> - due 2.3.25 (Monday going forward)',
  ' ',

     "Week 4 <br> 2.10.25", 'Data Wrangling', 
  '{{< fa book-open >}} <a href="https://r4ds.had.co.nz/transform.html" target = "_blank"> R4DS Transform</a> <br> {{< fa book-open >}} <a href="https://st47s.com/DS002R/Notes/07-wrangling.html" target = "_blank">wrangling</a> <br> {{< fa desktop >}} <a href="https://ds002r-fds.netlify.app/slides/2025-02-05-verbs.html" target = "_blank"> Data Verbs</a> <br> {{< fa desktop >}} <a href="https://ds002r-fds.netlify.app/slides/2025-02-10-pivotjoin.html" target = "_blank"> Pivot + Join</a> <br> {{< fa pencil >}} <a href="https://ds002r-fds.netlify.app/handout/ws6_ds2_s25_join.pdf" target = "_blank">WS 6 - Joining</a>',

    '{{< fa code >}} <a href="https://github.com/orgs/ST47S-FODS-Spring2025/repositories" target = "_blank">HW 3</a> - due 2.10.25 <br> Quiz 1 2.12.25',
  ' ',

  
     "Week 5 <br> 2.17.25", 'Data Types', 
  '{{< fa book-open >}} <a href="https://r4ds.hadley.nz/factors" target = "_blank"> R4DS Factors</a> <br> {{< fa book-open >}} <a href="https://r4ds.hadley.nz/strings" target = "_blank"> R4DS Strings</a> <br> {{< fa book-open >}} <a href="https://st47s.com/DS002R/Notes/08-text-analysis.html" target = "_blank">Text analysis</a> <br> {{< fa desktop >}} <a href="https://ds002r-fds.netlify.app/slides/2025-02-17-types.html" target = "_blank">Data Types</a> <br> {{< fa pencil >}} <a href="https://ds002r-fds.netlify.app/handout/ws7_ds2_s25_strings.pdf" target = "_blank">WS 7 - String Variables</a> <br> {{< fa pencil >}} <a href="https://ds002r-fds.netlify.app/handout/ws8_ds2_s25_factors.pdf" target = "_blank">WS 8 - Factor Variables</a>',

  '{{< fa code >}} <a href="https://ds002r-fds.netlify.app/project1">Project 1</a> - due 2.19.25',
  ' ',

  
     "Week 6 <br> 2.24.25", 'Regular Expressions', 
  '{{< fa book-open >}} <a href="https://r4ds.hadley.nz/regexps.html" target = "_blank"> R4DS Regular expressions</a> <br> {{< fa book-open >}} <a href="https://st47s.com/DS002R/Notes/09-reg-expr.html" target = "_blank">Regular expressions</a> <br> {{< fa desktop >}} <a href="https://ds002r-fds.netlify.app/slides/2025-02-24-regex.html" target = "_blank">Regular expressions</a> <br> {{< fa pencil >}} <a href="https://ds002r-fds.netlify.app/handout/ws9_ds2_s25_regex1.pdf" target = "_blank">WS 9 - Regular Expressions</a> ',

  '{{< fa code >}} <a href="https://github.com/orgs/ST47S-FODS-Spring2025/repositories" target = "_blank">HW 4</a> - due 2.25.25 (Tuesday going forward) <br> Quiz 2 2.26.25',
  ' ',

  
     "Week 7 <br> 3.3.25", 'functions + <br> iteration', 
  '{{< fa book-open >}} <a href="https://r4ds.hadley.nz/functions" target = "_blank"> R4DS Fuctions</a> <br>  {{< fa book-open >}} <a href="https://r4ds.hadley.nz/iteration" target = "_blank"> R4DS Iteration</a> <br>  {{< fa book-open >}} <a href="https://st47s.com/DS002R/Notes/12-iteration.html" target = "_blank">Functions + Iteration</a> <br> {{< fa desktop >}} <a href="https://ds002r-fds.netlify.app/slides/2025-03-03-funcmap.html" target = "_blank">functions + iteration</a> <br> {{< fa pencil >}} <a href="https://ds002r-fds.netlify.app/handout/ws10_ds2_s25_funcs.pdf" target = "_blank">WS 10 - Functions</a> <br> {{< fa pencil >}} <a href="https://ds002r-fds.netlify.app/handout/ws11_ds2_s25_map.pdf" target = "_blank">WS 11 - map</a>',

    '{{< fa code >}} <a href="https://ds002r-fds.netlify.app/project2">Project 2</a> - due 3.5.25',
  ' ',

  
     "Week 8 <br> 3.10.25", 'code review + <br> reprex', 
 '{{< fa book-open >}} <a href="https://www.tidyverse.org/help/" target = "_blank"> reproducible examples</a> <br>  {{< fa book-open >}} <a href="https://style.tidyverse.org/" target = "_blank"> Tidyverse style guide</a> <br>  {{< fa book-open >}} <a href="https://st47s.com/DS002R/Notes/16-reprex.html" target = "_blank">Reproducible examples</a> <br> {{< fa desktop >}} <a href="https://ds002r-fds.netlify.app/slides/2025-03-10-help.html" target = "_blank">help me help you</a> <br> {{< fa pencil >}} <a href="https://ds002r-fds.netlify.app/handout/ws12_ds2_s25_reprex.pdf" target = "_blank">WS 12 - help me help you</a> <br> {{< fa pencil >}} <a href="https://ds002r-fds.netlify.app/handout/ws13_ds2_s25_probsim.pdf" target = "_blank">WS 13 - probability sim</a>',
  '{{< fa code >}} <a href="https://github.com/orgs/ST47S-FODS-Spring2025/repositories" target = "_blank">HW 5</a> - due 3.11.25',
  ' ',

"3.17.25", 'Spring Break', ' ', ' ', ' ',
  
     "Week 9 <br> 3.24.25", 'iterations + <br> simulations', 
 '{{< fa book-open >}} <a href="https://mdsr-book.github.io/mdsr3e/13-simulation.html" target = "_blank"> MDSR Simulations</a> <br> {{< fa book-open >}} <a href="https://st47s.com/DS002R/Notes/12-iteration.html" target = "_blank">Iterations</a> <br> {{< fa desktop >}} <a href="https://ds002r-fds.netlify.app/slides/2025-03-12-iters.html" target = "_blank">Iterations</a> <br> {{< fa pencil >}} <a href="https://ds002r-fds.netlify.app/handout/ws14_ds2_s25_model-sim.pdf" target = "_blank">WS 14 - model simulation</a> <br> {{< fa pencil >}} <a href="https://ds002r-fds.netlify.app/handout/ws15_ds2_s25_helper.pdf" target = "_blank">WS 15 - helper & hinderer</a>',
  '{{< fa code >}} <a href="https://github.com/orgs/ST47S-FODS-Spring2025/repositories" target = "_blank">HW 6</a> - due 3.25.25 <br> Quiz 3 3.26.25',

  ' ',

  
     "Week 10 <br> 3.31.25", 'permutation tests', 
 '{{< fa book-open >}} <a href="https://st47s.com/DS002R/Notes/13-permutation-tests.html" target = "_blank">Permutation tests</a> <br> {{< fa desktop >}} <a href="https://ds002r-fds.netlify.app/slides/2025-03-26-perm.html" target = "_blank">Permutation tests</a> <br> {{< fa desktop >}} <a href="https://ds002r-fds.netlify.app/slides/2025-04-02-ethics.html" target = "_blank">Data Science Ethics</a> <br> {{< fa pencil >}} <a href="https://ds002r-fds.netlify.app/handout/ws16_ds2_s25_permtest.pdf" target = "_blank">WS 16 - permutation test</a> <br> {{< fa pencil >}} <a href="https://ds002r-fds.netlify.app/handout/ws17_ds2_s25_ethics.pdf" target = "_blank">WS 17 - ethics</a>',
  '{{< fa code >}} <a href="https://ds002r-fds.netlify.app/project3">Project 3</a> - due 4.2.25',
  ' ',
  
  
     "Week 11 <br> 4.7.25", 'web scraping', 
 '{{< fa book-open >}} <a href="https://r4ds.hadley.nz/webscraping" target = "_blank">R4DS Web scraping</a> <br> {{< fa book-open >}} <a href="https://st47s.com/DS002R/Notes/03-rvest.html" target = "_blank">Web scraping</a> <br> {{< fa desktop >}} <a href="https://ds002r-fds.netlify.app/slides/2025-04-07-webscrape.html" target = "_blank">Web scraping</a> <br> {{< fa pencil >}} <a href="https://ds002r-fds.netlify.app/handout/ws18_ds2_s25_css.pdf" target = "_blank">WS 18 - css selectors</a>',
  '{{< fa code >}} <a href="https://github.com/orgs/ST47S-FODS-Spring2025/repositories" target = "_blank">HW 7</a> - due 4.8.25 <br> Quiz 4 4.9.25',

  ' ',
  
  
     "Week 12 <br> 4.14.25", 'SQL', 
 '{{< fa book-open >}} <a href="https://r4ds.hadley.nz/databases.html" target = "_blank">R4DS Databases</a> <br> {{< fa book-open >}} <a href="https://mdsr-book.github.io/mdsr3e/15-sqlI.html" target = "_blank">MDSR Database querying</a> <br> {{< fa book-open >}} <a href="https://st47s.com/DS002R/Notes/04-sql-in-R.html" target = "_blank">SQL</a> <br> {{< fa desktop >}} <a href="https://ds002r-fds.netlify.app/slides/2025-04-14-db.html" target = "_blank">SQL DBMS</a> <br> {{< fa desktop >}} <a href="https://ds002r-fds.netlify.app/slides/2025-04-16-clauses.html" target = "_blank">SQL statements</a> <br> {{< fa pencil >}} <a href="https://ds002r-fds.netlify.app/handout/ws19_ds2_s25_sql1.pdf" target = "_blank">WS 19 - SQL database</a> <br> {{< fa pencil >}} <a href="https://ds002r-fds.netlify.app/handout/ws20_ds2_s25_sql2.pdf" target = "_blank">WS 20 - SQL statements</a>',
   '{{< fa code >}} <a href="https://ds002r-fds.netlify.app/project4">Project 4</a> - due 4.16.25',
  ' ',
  
  
     "Week 13 <br> 4.21.25", 'SQL', 
 '{{< fa book-open >}} <a href="https://r4ds.hadley.nz/databases.html" target = "_blank">R4DS Databases</a> <br> {{< fa book-open >}} <a href="https://mdsr-book.github.io/mdsr3e/15-sqlI.html" target = "_blank">MDSR Database querying</a> <br> {{< fa book-open >}} <a href="https://st47s.com/DS002R/Notes/06-sql-joins.html" target = "_blank">SQL joins</a> <br> {{< fa desktop >}} <a href="https://ds002r-fds.netlify.app/slides/2025-04-21-joins.html" target = "_blank">SQL joins</a> <br> {{< fa pencil >}} <a href="https://ds002r-fds.netlify.app/handout/ws21_ds2_s25_sql3.pdf" target = "_blank">WS 21 - writing SQL</a>',
  '{{< fa code >}} <a href="https://github.com/orgs/ST47S-FODS-Spring2025/repositories" target = "_blank">HW 8</a> - due 4.22.25 <br> Quiz 5 4.23.25',
  ' ',

     "Week 14 <br> 4.28.25", 'Shiny', 
  '{{< fa book-open >}} <a href="https://mastering-shiny.org/" target = "_blank">Matering Shiny</a> <br> {{< fa book-open >}} <a href="https://mdsr-book.github.io/mdsr3e/14-datavizIII.html#sec-shiny" target = "_blank">MDSR Interactive web apps with Shiny</a> <br> {{< fa book-open >}} <a href="https://st47s.com/DS002R/Notes/12-shiny.html" target = "_blank">Shiny</a> <br> {{< fa desktop >}} <a href="https://ds002r-fds.netlify.app/slides/2025-04-30-shiny.html" target = "_blank">Shiny</a> <br> {{< fa pencil >}} <a href="https://ds002r-fds.netlify.app/handout/ws22_ds2_s25_sql4.pdf" target = "_blank">WS 22 - SQL Joins</a> <br> {{< fa pencil >}} <a href="https://ds002r-fds.netlify.app/handout/ws23_ds2_s25_shiny.pdf" target = "_blank">WS 23 - Shiny</a>',
  '{{< fa code >}} <a href="https://ds002r-fds.netlify.app/project5">Project 5</a> - due 4.30.25',
  ' ',

      "Week 15 <br> 5.5.25", ' ', 
  '{{< fa desktop >}} <a href="https://ds002r-fds.netlify.app/slides/2025-05-05-fin.html" target = "_blank">Fin</a> ',
   'Quiz 6 5.7.25',
  'presentations (?) 5.8.25',
  
    "Week 16 <br> 5.13.25", ' ', 
  ' ',
  '{{< fa code >}} <a href="https://ds002r-fds.netlify.app/project5">Project 6</a> - due 5.13.25 <br> + presentations (?)',
  ' '
)
  
```

```{r}
#| echo: false
#| column: screen-inset
# can also use column: screen-inset also the entire page??
# can use column: page for the entire page
# can use column: body-outset to bleed outside the center column of text
schedule |> 
  gt::gt() |> 
  gt::fmt_markdown(columns = everything()) |> 
    gt::cols_width(date ~ pct(8),
                 everything() ~ pct(23)) 
```





