---
title: "Project 2"
description: |
  Completing a full text analysis
format: html
---

### Overview

You will find a data set containing string data.  This could be newspaper articles, tweets, songs, plays, movie reviews, or anything else you can imagine.  Then you will answer questions of interest and tell a story about your data using string and regular expression skills you have developed.

Your analysis must contain the following elements:

- at least 3 `str_*()` functions
- at least 3 regular expressions
- at least 2 illustrative, well-labeled plots or tables
- a description of what insights can be gained from your plots and tables
- a reference / documentation of the data source.


Logistics:

- please include all the code used in the analysis.
- make sure that all graphs are well-labeled (including x and y axes, title of the graph, and labels for color or fill).
- do not include superfluous error or warning messages.
- include a few sentences describing each of your plots or tables.  That is, tell the reader what they see when they look at the plot. Your narrative description should be in the text part of the qmd file, not as a comment in an R chunk.


### Some potential places to find text data

I've gathered some potential datasets for you to work with.  All of the datasets below contain some or a lot of text.

* <a href = "https://github.com/rfordatascience/tidytuesday/blob/master/data/2024/2024-09-17/readme.md" target = "_blank"> Shakespeare Dialogue</a> 

* <a href = "https://github.com/rfordatascience/tidytuesday/blob/master/data/2021/2021-04-20/readme.md" target = "_blank">Netflix titles</a>

* <a href = "https://github.com/rfordatascience/tidytuesday/blob/master/data/2020/2020-04-28/readme.md" target = "_blank">synopses data frame</a> for Broadway Weekly Grosses

* <a href = "https://github.com/EmilHvitfeldt/friends" target = "_blank">Friends dialogue</a>

* <a href = "https://github.com/nicholasjhorton/FederalistPapers/" target = "_blank">Federalist Papers</a>
   - Load the package into R using
   
```{r}
#| eval: false
install.packages("devtools")
devtools::install_github("nicholasjhorton/FederalistPapers")
```


* All of <a href = "https://github.com/Amherst-Statistics/DickinsonPoems" target = "_blank">Emily Dickinson's poems</a>
    - Load the package into R using
    
```{r}
#| eval: false
devtools::install_github("Amherst-Statistics/DickinsonPoems")
```

* <a href = "https://www.kaggle.com/datasets/fabriziocominetti/the-office-lines" target = "_blank">Every line of the office</a>

* All of <a href = "https://www.obamalibrary.gov/digital-research-room/archived-white-house-websites-and-social-media" target = "_target">Barack Obama's tweets</a> archived by the National Archives.

* The "Dear Abby" stories underlying The Pudding’s <a href = "https://pudding.cool/2018/11/dearabby/" target = "_blank">30 Years of American Anxieties article</a>
    - See data on the <a href = "https://github.com/the-pudding/data/tree/master/dearabby" target = "_blank">The Pudding's GitHub site</a>
    - Load the data in using
    
```{r}
#| eval: false
read_csv("https://raw.githubusercontent.com/the-pudding/data/master/dearabby/raw_da_qs.csv")
```

- <a href = "https://github.com/the-pudding/data" target = "_blank">Other articles from The Pudding</a>

- NY Times headlines from the RTextTools package (see below)

```{r}
#| eval: false

library(RTextTools) 
data(NYTimes)
as_tibble(NYTimes)
```

- the options are endless -- be resourceful and creative!


### Timeline

Mini-Project 2 must be submitted on Canvas (not Gradescope) by **11:59 PM on Wednesday October 2**.  Ideally, you will add a tab to your Quarto webpage for Mini-Project 2, then you can just submit the new page's URL. Alternatively, you may submit a Rendered pdf showing all code and output.