---
title: "Project 2"
description: |
  Completing a full text analysis
format: html
---


### Overview

You will find a data set containing string / character data.  The data could be on newspaper articles, tweets, songs, scripts, movie reviews, or anything else you can imagine.  Then you will answer questions of interest and tell a story about your data using the string and regular expression skills you have developed.

Your analysis must contain the following elements:

- at least 3 `str_*()` functions (3 different functions)
- at least 3 regular expressions
- at least 1 lookaround
- at least 2 illustrative, well-labeled plots or tables
- a description of what insights can be gained from your plots and tables
- a reference / documentation of the data source.


Logistics:

- please include all your code used in the analysis (but feel free to use code folding^[code folding allows the user can see the code if they want to: https://quarto.org/docs/output-formats/html-code.html#folding-code].)
- make sure that all graphs are well-labeled (including x and y axes, title of the graph, and accurate and succinct labels for color and fill).
- do not include error or warning messages (see HW YAML for code).
- include a few sentences describing each of your plots or tables.  That is, tell the reader what they see when they look at the plot. Your narrative description should be in the text part of the qmd file, not as a comment in an R chunk.
- please include the source of the data (which might include, for example, both the link to the data source (e.g., TidyTuesday page) + the original source of the data (e.g., NYT)).


### Some potential places to find text data

I've gathered some potential datasets for you to work with.  All of the datasets below contain some or a lot of text.

* <a href = "https://github.com/rfordatascience/tidytuesday/blob/master/data/2024/2024-09-17/readme.md" target = "_blank"> Shakespeare Dialogue</a> 

* <a href = "https://github.com/rfordatascience/tidytuesday/blob/master/data/2021/2021-04-20/readme.md" target = "_blank">Netflix titles</a>

* <a href = "https://github.com/rfordatascience/tidytuesday/blob/master/data/2020/2020-04-28/readme.md" target = "_blank">synopses data frame</a> for Broadway Weekly Grosses

* <a href = "https://github.com/EmilHvitfeldt/friends" target = "_blank">Friends dialogue</a>

* <a href = "https://github.com/nicholasjhorton/FederalistPapers/" target = "_blank">Federalist Papers</a>
   - Load the package into R using
   
```{r}
#| eval: false
install.packages("devtools")
devtools::install_github("nicholasjhorton/FederalistPapers")
```


* All of <a href = "https://github.com/Amherst-Statistics/DickinsonPoems" target = "_blank">Emily Dickinson's poems</a>
    - Load the package into R using
    
```{r}
#| eval: false
devtools::install_github("Amherst-Statistics/DickinsonPoems")
```

* <a href = "https://www.kaggle.com/datasets/fabriziocominetti/the-office-lines" target = "_blank">Every line of the office</a>

* All of <a href = "https://www.obamalibrary.gov/digital-research-room/archived-white-house-websites-and-social-media" target = "_target">Barack Obama's tweets</a> archived by the National Archives.

* The "Dear Abby" stories underlying The Pudding’s <a href = "https://pudding.cool/2018/11/dearabby/" target = "_blank">30 Years of American Anxieties article</a>
    - See data on the <a href = "https://github.com/the-pudding/data/tree/master/dearabby" target = "_blank">The Pudding's GitHub site</a>
    - Load the data in using
    
```{r}
#| eval: false
read_csv("https://raw.githubusercontent.com/the-pudding/data/master/dearabby/raw_da_qs.csv")
```

- <a href = "https://github.com/the-pudding/data" target = "_blank">Other articles from The Pudding</a>

- NY Times headlines from the RTextTools package (see below)

```{r}
#| eval: false

library(RTextTools) 
data(NYTimes)
as_tibble(NYTimes)
```

- the options are endless -- be resourceful and creative!


### Timeline

Mini-Project 2 must be submitted on Canvas (not Gradescope) by **11:59 PM on Wednesday March 5**.  You will add a tab to your Quarto webpage for Mini-Project 3 and submit the new page's URL.

